### 2018-08-28 paper/finitecomplete-failures.tex
Complexity considerations improved

>>>>

% ==========================================================================
\subsection{Complexity Considerations}
\label{sec:complexity}

As can be seen from the specification of the test cases $U_F(k)$, the number of 
executions ending in a $\epass$-event corresponds to the number $\ell$ of traces $s$ 
of $P$ with length equal to\footnote{In this estimation, we disregard 
the case where the test
terminates earlier due to entering branch (\ref{eq:ufb}).} $k$, 
multiplied by the number $h$ of minimal hitting sets in
$\minhits(P/s)$. The first factor 
has worst-case upper bound $\ell\le |\Sigma|^k$.

Given a set $\minaccs(P/s) = \{ A_1,\dots, A_a \}$ of   minimal acceptances,
the cardinality $h$ of $\minhits(P/s)$ is maximal for the case where all $A_i$ are disjoint.
In this case,  $h=|\minhits(P/s)| = \prod_{i=1}^a|A_i|$. To find an upper bound for $h$, 
we need to solve the constrained optimisation problem
\[
\text{maximise}\ \prod_{i=1}^a|A_i| \ \text{under constraint}\ \sum_{i=1}^a|A_i| = |\Sigma|
\wedge \bigwedge_{i=1}^a |A_i| > 0
\]
For fixed $a$, this can be solved using Lagrange multipliers, but there is no 
closed expression for the maximum value to be achieved when the $|A_i|$ 
and $a$ are considered as 
unknown variables. Therefore, we only note that $h=|\minhits(P/s)|$ is significantly smaller
than $2^{|\Sigma|}$, because for every $H\in  \minhits(P/s)$, all of its true subsets and true supersets are {\it not} contained in $\minhits(P/s)$. This leaves us with an estimate
for the worst-case upper bound of $h\cdot |\Sigma|^k$ with $h\ll 2^{|\Sigma|}$.
According to Theorem~\ref{th:failurestest},
we need to execute these test for $k = 0,\dots,(pq-1)$; this results in a worst-case bound
of (we use the formula for the sum of the geometric progression here)
\[
h\cdot \big( \frac{1-|\Sigma|^{pq}}{1-|\Sigma|} \big),\
 \text{or, asymptotically,}\  O(h\cdot2^{(pq-1)}), 
 \  \text{with}\ h\ll 2^{|\Sigma|}.
\]

From Lemma~\ref{lemma:hseta} we know that 
 the worst-case bound $h\ll 2^{|\Sigma|}$ cannot be further improved, since 
the full collection of minimal hitting sets needs to be checked in order to verify
the $conf$ relation.

The authors of~\cite{Hennessy:1988:ATP:50497} and \cite{DBLP:conf/icfem/CavalcantiG07} 
suggest to test {\it every}
non-empty 
subset of $\Sigma$ whose events cannot be completely refused in a given process state
of the reference model; this leads to a worst-case estimate of $2^{|\Sigma|}$
for the number of different sets to be offered to the SUT in the last step of 
the test execution, so our approach reduces the number of test executions in comparison
 to~\cite{Hennessy:1988:ATP:50497,DBLP:conf/icfem/CavalcantiG07}.

It is discussed in Section~\ref{sec:conc} that the term $pq$ occurring in this bound can be significantly reduced by using more complex test cases that need not execute {\it all} 
traces of $P$ with length less or equal to $pq$.

### 2018-08-28 paper/introduction.tex
Complexity considerations improved

The main contribution of this paper consists in the construction of two test suites
verifying the conformance relations \emph{trace refinement} and  \emph{failures refinement}, respectively, for any given non-divergent, finite-state, finite alphabet 
CSP reference process. We prove their completeness with respect to fault domains
of the described type.  The
existence of -- possibly infinite -- complete test suites has been
established for process algebras, and for CSP in particular, by several
authors~\cite{Hennessy:1988:ATP:50497,Schneider:1995:OST:203471.203475,DBLP:conf/fm/PeleskaS96,peleska1997a,DBLP:conf/pts/CavalcantiS17}.
To the best of our knowledge, however, this article is the first to present
{\it finite}, complete test suites associated with this class of fault
domains and conformance relations.

>>>>

The main contribution of this paper consists in the construction of two test suites
verifying the conformance relations \emph{trace refinement} and  \emph{failures refinement}, respectively, for any given non-divergent, finite-state, finite alphabet 
CSP reference process. We prove their completeness with respect to fault domains
of the described type.  The
existence of -- possibly infinite -- complete test suites has been
established for process algebras, and for CSP in particular, by several
authors~\cite{Hennessy:1988:ATP:50497,Schneider:1995:OST:203471.203475,DBLP:conf/fm/PeleskaS96,peleska1997a,DBLP:conf/icfem/CavalcantiG07,DBLP:conf/pts/CavalcantiS17}.
To the best of our knowledge, however, this article is the first to present
{\it finite}, complete test suites associated with this class of fault
domains and conformance relations.

### 2018-08-28 paper/preliminaries.tex
Complexity considerations improved

Summarising, refinement relations between finite-state CSP processes $P, Q$ can be be
expressed by means of their normalised transition graphs 
$$G(P) = ( N_P, {\ii n}_P, \Sigma, t_P : N_P\times\Sigma \pfun N_P, r_P : N_P \fun \mathbb{P}\mathbb{P}(\Sigma))$$ 
and 
$$G(Q) = ( N_Q, {\ii n}_Q, \Sigma, t_Q : N_Q\times\Sigma \pfun N_Q, r_Q : N_Q \fun \mathbb{P}\mathbb{P}(\Sigma))$$
in the following
way. 
\begin{lemma}
  \label{lemma:tgtrcref}
  \begin{eqnarray}
  P \lessdet_T Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P))
  \label{eq:trcrefa}
  \\
  \label{eq:failconf}
  P \lessdet_F Q & \Leftrightarrow & P \lessdet_T Q \wedge P\ conf\ Q
  \\
  \label{eq:failrefa}
  P\ conf\ Q & \Leftrightarrow & \nonumber
  \forall s\in\trc(G(Q))\cap \trc(G(P)), R_Q\in r_Q(G(Q)/s):  \nonumber
  \\ & & \tabd
  \exists R_P\in r_P(G(P)/s): R_Q\subseteq R_P
  \\
  \label{eq:failrefb}
   & \Leftrightarrow & 
    \forall s\in\trc(G(Q))\cap \trc(G(P)), A_Q\in\minaccs(G(Q)/s):  \nonumber
   \\ & & \tabd
  \exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
 \end{eqnarray}
  \xbox
\end{lemma}

>>>>

Summarising, refinement relations between finite-state CSP processes $P, Q$ can be be
expressed by means of their normalised transition graphs 
\begin{eqnarray*}
G(P) & = & ( N_P, {\ii n}_P, \Sigma, t_P : N_P\times\Sigma \pfun N_P, r_P : N_P \fun \mathbb{P}\mathbb{P}(\Sigma))
\\
G(Q) & = & ( N_Q, {\ii n}_Q, \Sigma, t_Q : N_Q\times\Sigma \pfun N_Q, r_Q : N_Q \fun \mathbb{P}\mathbb{P}(\Sigma))
\end{eqnarray*}
%
in the following
way. 
\begin{lemma}
  \label{lemma:tgtrcref}
  \begin{eqnarray}
  P \lessdet_T Q & \Leftrightarrow & \trc(G(Q)) \subseteq\trc(G(P))
  \label{eq:trcrefa}
  \\
  \label{eq:failconf}
  P \lessdet_F Q & \Leftrightarrow & P \lessdet_T Q \wedge P\ conf\ Q
  \\
  \label{eq:failrefa}
  P\ conf\ Q & \Leftrightarrow & \nonumber
  \forall s\in\trc(G(Q))\cap \trc(G(P)), R_Q\in r_Q(G(Q)/s):  \nonumber
  \\ & & \tabd
  \exists R_P\in r_P(G(P)/s): R_Q\subseteq R_P
  \\
  \label{eq:failrefb}
   & \Leftrightarrow & 
    \forall s\in\trc(G(Q))\cap \trc(G(P)), A_Q\in\minaccs(G(Q)/s):  \nonumber
   \\ & & \tabd
  \exists A_P\in\minaccs(G(P)/s): A_P\subseteq A_Q
 \end{eqnarray}
  \xbox
\end{lemma}
